NumPy---Array Computation for Python

### 2019-12-18 paper.tex
ENH: Add URL for randomgen
Add URL and reformat

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\code{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator\cite{random123} (\code{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator\cite{practrand} (\code{SFC64}), and the 32-bit
Mersenne Twister\cite{mt19937} (\code{MT19937}) which has been used in older
versions of NumPy.\footnote{The randomgen project supplies a wide range of
alternative bit generators such as a cryptographic counter-based generators
(\code{AESCtr}) and generators that expose hardware random number generators
(\code{RDRAND})\cite{randomgen}.} Bit generators export a capsule containing
pointers to functions that produce 64 bits, 32 bits, or a random double. They
also expose CFFI and ctypes interfaces to the same three functions.

>>>>

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\code{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator\cite{random123} (\code{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator\cite{practrand} (\code{SFC64}), and the 32-bit
Mersenne Twister\cite{mt19937} (\code{MT19937}) which has been used in older
versions of NumPy.\footnote{The
\href{https://github.com/bashtage/randomgen}{randomgen project} supplies a wide
range of alternative bit generators such as a cryptographic counter-based
generators (\code{AESCtr}) and generators that expose hardware random number
generators (\code{RDRAND})\cite{randomgen}.} Bit generators export a capsule
containing pointers to functions that produce 64 bits, 32 bits, or a random
double. They also expose CFFI and ctypes interfaces to the same three functions.
